A dynamic programing algorithm to assess the reliability of inferences from network enrichment analysis

### 2018-05-02 doc/genesetdp.tex
added plot
fix plot

We dowloaded network definitions and the BinoX software version FIXME for comparisons from XXX \url{bitbucket/sonnhammerlab}. FIXME: add a more detailed description of the test set (i.e. organism and number of genes, pathways and network connections).

@@

To illustrate the $p$~value calculation procedure we plotted the score distribution N(s) for a query size of 10 (FIXME) genes in Figure \ref{fig:score_dist}.

\begin{figure}[htb]
  {\em FIXME: Add this figure.}
%\includegraphics{img/FIXME.png}
  \caption{{\bf Score distribution of a query size of 10 genes.} GeneSetDP enables us to calculate the full score distribution for a query of a given size, $Q$, i.e. how many ways one can reach a certain score when adding up the scores for $Q$ genes.}
  \label{fig:score_dist}
\end{figure}

@@

In order to test the statistical calibration of our method, we calculated $p$~values for FIXME random picks of gene sets from the investigated genome. As our selection is random, and following our null hypothesis, we expected the resulting $p$~values to be uniformly distributed. To test this we plotted the $p$~values against their quantile in Figure \ref{fig:calibration}. As a comparison we also added a calibration curve for the popular NEA method BinoX\cite{ogris2016novel}.

@@

\begin{figure}[htb]
  {\em FIXME: Make a loglog plot of the relative rank and pvalues of GeneSetDP and BinoX. Add filled lines for y=x, and dotted lines for y=2x and y=0.5x.}
%\includegraphics{img/FIXME.png}
  \caption{{\bf Calibration of GeneSetDP.} We selected FIXME random sets from the investigated genome definition, and calculated their $p$ values with GeneSetDP. To test the $p$~values uniformity we plotted them against their quantile. We also added the calibration curve of BinoX, evaluated on the same random sets.}
  \label{fig:calibration}
\end{figure}

>>>>

We dowloaded network definitions and the BinoX software (on 2018/04/28) for comparisons from XXX \url{bitbucket/sonnhammerlab}. FIXME: add a more detailed description of the test set (i.e. organism and number of genes, pathways and network connections).

@@

To illustrate the $p$~value calculation procedure we plotted the score distribution N(s) for a query size of 10 genes in Figure \ref{fig:score_dist}.

\begin{figure}[htb]
		\begin{center}
				\includegraphics[scale=0.8]{figures/F1_score_distribuition.png}
		\end{center}
%\includegraphics{img/FIXME.png}
  \caption{{\bf Score distribution of a query size of 10 genes.} GeneSetDP enables us to calculate the full score distribution for a query of a given size, $Q$, i.e. how many ways one can reach a certain score when adding up the scores for $Q$ genes.}
  \label{fig:score_dist}
\end{figure}

@@

In order to test the statistical calibration of our method, we calculated $p$~values for 10000 random picks of gene sets from the investigated genome. As our selection is random, and following our null hypothesis, we expected the resulting $p$~values to be uniformly distributed. To test this we plotted the $p$~values against their quantile in Figure \ref{fig:calibration}. As a comparison we also added a calibration curve for the popular NEA method BinoX\cite{ogris2016novel}.

@@

\begin{figure}[htb]
		\begin{center}
				\includegraphics[scale=0.8]{figures/F2_calibration.png}
		\end{center}

%\includegraphics{img/FIXME.png}
  \caption{{\bf Calibration of GeneSetDP.} We selected 10000 random sets from the investigated genome definition, and calculated their $p$ values with GeneSetDP. To test the $p$~values uniformity we plotted them against their quantile. We also added the calibration curve of BinoX, evaluated on the same random sets.}
  \label{fig:calibration}
\end{figure}
